### 2015-11-05 CVPR16/Source/applications.tex

Let the pose of object $i$ at time $t$ be $\relp{i}{t}$. We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the projection and inverse projection functions that project a 3D point to the camera image and vice versa. Then, the reprojection error for the $j$\textsuperscript{th} 2D point, with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on object pose at time $t-1$ while the forward projection depends on pose at time $t$ which can be different.

For an object $i$, let $\{ \relp{i}{t} \}_i$ be the poses of all occluding objects at time $t$ and $ \{ \dimsn{i} \}_i$ be their dimensions. Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
\begin{multline}
  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of the $j$\textsuperscript{th} point with the $i$\textsuperscript{th} object at depth $\lambda$, given by \eqref{eq:defineassocP}.

@@

Object detection is usually followed by non-maximal suppression that results in
discarding similar bounding boxes. When we are jointly optimizing detections
with other cues, it is not usually desirable to go with a single bounding box.
Hence, we keep all the bounding box detections by approximating them with
multi-modal sum of Gaussian like logistic functions. We fit the parametric function of the form 
%
\begin{multline}
  S(\bb{i}) = \\
  \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
  (\bb{i}-\mu^{(d)}_k))
\end{multline}
%
to detection scores, by non-linear error minimization with initialization from
non-maximal suppressed outputs. Here $\mu^{(d)}_j$ is one of the $k$ modes as a
4D vector representing a single bounding box as $[\minx, \miny, \maxx,
\maxy]^\top$. The optimization is constrained with symmetry and positive
definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ on image be occluded assuming
the point is on traffic participant (TP) $i$ with mean depth $\mu^{(i)}_d$ as
\begin{align}
  O_{i}(\u, \mu^{(i)}_d) = 1 - \Ptransmission(\mu^{(i)}_d\u) \enspace .
\end{align}

If we know a portion of our proposed detection bounding box is known to be
occluded, then we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundary of detection bounding boxes, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion we sample
$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
GMM $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
  $\Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j$.
The detection scores GMM with occlusion is given by replacing the covariance
matrix
%
\begin{multline}
  S'(\bb{i}) =
  \\
  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{multline}

>>>>

Let the pose of object $i$ at time $t$ be $\relp{i}{t}$. We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the forward and inverse projection functions that project a 3D point to the camera image and vice versa. Then, the reprojection error for the $j$\textsuperscript{th} 2D point, $\trackp{t}$, with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on object pose at time $t-1$ while the forward projection depends on pose at time $t$, which can be different.

For an object $i$, let $\{ \Omega (t) \}_i$ be the poses of all occluding objects at time $t$ (inclusive of object $i$) and $ \{ \bB \}_i$ be their dimensions. Then, we model the continuous point tracks energy with explicit occlusion reasoning as the expected reprojection error over the association probability:
\begin{multline}
  %\!\!\!\! \Energy{track}(\relp{i}{t}, \relp{i}{t-1}, \dimsn{i}, \{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i ) 
  %\Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \Energy{track}(\{ \Omega (t) \}_i, \{ \Omega (t-1) \}_i, \{ \bB \}_i )
  \\
    = \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of the $j$\textsuperscript{th} point with the $i$\textsuperscript{th} object at depth $\lambda$, given by \eqref{eq:defineassocP}.

@@

Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is not usually desirable to go with a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions. In particular, let $\bb{i}$ be a detection bounding box for object $i$, parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{(i)}(t)^\top \Lambda_k^{-1} \bepsilon_k^{(i)}(t) \right)
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{(i)}(t) = \bb{i}-\mu^{(k)}_d$, with $\mu^{(k)}_d$ the mean and $\Lambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\Lambda_k^{-1}$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

\paragraph{Detection scores with occlusion reasoning} 
\def\u{\mathbf{u}}
With our model of $\Ptrans$ described in Section \ref{sec:ptransmission}, we can
compute the probability of a point $\u$ in the image to be occluded assuming
the point is on object $i$ with mean depth $\mu^{(i)}_d$ as
\begin{align}
  O_{i}(\u, \mu^{(i)}_d) = 1 - \Ptransmission(\mu^{(i)}_d\u) \enspace .
\end{align}

If a portion of our proposed detection bounding box is known to be
occluded, then we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundary of detection bounding boxes, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
To re-model our detection scores scaled by continuous occlusion we sample
$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
GMM $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
  $\Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j$.
The detection scores GMM with occlusion is given by replacing the covariance
matrix
%
\begin{multline}
  S'(\bb{i}) =
  \\
  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{multline}

### 2015-11-05 CVPR16/Source/intro.tex

In this work, we first propose to model objects as 3D ellipsoids. Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions. Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}. As we will show later, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for tackling occlusions. Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art motion segmentation methods~\cite{Rao_etal_2010,Brox_Malik_2010}.

As an important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving. In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., $\{0,1\}$ probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [$0,1$] probabilities). Consequently, it offers a unified continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective optimization tools. As we will show in the experiments, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of~\cite{Song_Chandraker_2014} which employs bounding boxes for point-to-object assignments.

>>>>

In this work, we first propose to model objects as 3D ellipsoids. Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions. Leveraging on the success of object detection and tracking algorithms~\cite{Felzenszwalb_etal_2010,Choi_Savarese_2010}, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets~\cite{Zach2007}, including both dynamic and static point tracks. As we will show in the experiments, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for dealing with occlusions. Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art motion segmentation methods~\cite{Rao_etal_2010,Brox_Malik_2010}.

As another important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving. In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., $\{0,1\}$ probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [$0,1$] probabilities). Consequently, it offers a \emph{unified} continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective continuous optimization tools. As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors compared to those of~\cite{Song_Chandraker_2014}, which employs bounding boxes for point-to-object associations.

### 2015-11-05 CVPR16/Source/related.tex

\section{Related Work}
\paragraph{Occlusion handling in tracking}
Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}. A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicits models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking. However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object. Our occlusion modeling is much more general in determining the probability of a point in space as belonging to an object. While it can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it can have far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.

\paragraph{3D localization and scene understanding}
One of the central goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes. For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology. Similar to us, other works have also considered monocular frameworks. Notably, occlusions are explicitly handled in \cite{Wojek_etal_2013} by considering partial object detectors. A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual occlusions between objects. In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space, which makes it more general, extensible and amenable for continuous optimization.

\paragraph{Motion segmentation and multibody SFM}
An application for our occlusion modeling is to determine point track associations in scenes with multiple objects. For moving objects, this is within the purview of motion segmentation, which has been actively studied \cite{Tron_Vidal_2007,Rao_etal_2010}. This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}. Motion segmentation is also used within multibody structure from motion (SFM) frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}. In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.

>>>>

\section{Related Work}
\label{sec:related}

%An application for our occlusion modeling is to determine point track associations in scenes with multiple objects. For moving objects, this is within the purview of motion segmentation, which has been actively studied \cite{Tron_Vidal_2007,Rao_etal_2010}. This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}. Motion segmentation is also used within multibody structure from motion (SFM) frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}. In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.

\paragraph{Motion segmentation}
Motion segmentation has actively been studied in the literature. Previous work can roughly be categorized into algebraic methods~\cite{}, statistical methods~\cite{} and clustering methods~\cite{}. Some recent efforts include robust algebraic segmentation with hybrid perspective constraints~\cite{} and spectral clustering with point track spatial affinity~\cite{}. The above methods usually exploit the fact that point tracks of a particular moving object tend to follow similar motion patterns. Therefore, they cannot segment static objects due to no motion cues. In contrast, our method is relatively independent of object motions and hence does not suffer from static objects.

\paragraph{Occlusion handling}
Occlusion handling plays an important role in many computer vision applications such as object detection and tracking. Methods that are capable of detecting occluded objects include~\cite{}, which trains different object part detectors, and~\cite{}, which learns 3D cues from a CAD database. These methods are either based on 2D cues~\cite{} or often a discrete representation of occlusion behavior~\cite{}. In contrast, our occlusion model is fully 3D and allows for a continuous representation. For object tracking, occlusions are often handled by a set of occluder patterns~\cite{}. A notable exception is~\cite{}, which explicitly models object occlusions in continuous domain to determine the visibility of each object. ...

%Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}. A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicits models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking. However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object. Our occlusion modeling is much more general in determining the probability of a point in space as belonging to an object. While it can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it can have far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.

\paragraph{3D localization}
One of the central goals of 3D scene understanding is to localize the 3D positions and orientations of objects in complex scenes. For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology. Similar to us, other works have also considered monocular frameworks. Notably, occlusions are explicitly handled in \cite{Wojek_etal_2013} by considering partial object detectors. A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014}, which also allows reasoning about mutual occlusions between objects. In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space, which makes it more general, extensible and amenable for continuous optimization.
